% !TEX root = main.tex
\section{Introduction}
\label{sect:introduction}
Design is often mentioned to be very important to achieve certain properties and characteristics of a software system. Although it is very important to have design documentation, developers usually do not produce design documentation that often. But they discuss about different aspects of design in various communication channel like Github pull requests, issue tracker or commits. The paper we are trying to replicate provides quantitative evidence that developers address design through discussions. The authors of the original paper have mainly tried to answer two research questions:
\begin{enumerate}
	\item To what extent do developers discuss design in open-source projects?
	\item Which developers discuss design?
\end{enumerate}
We are trying to strictly replicate the steps to answer those two research questions. In the process of answering the two main research questions, we are also answering some auxiliary research questions such as: \noindent\textbf{(a)} the ratio between design discussions vs contributors, \noindent\textbf{(b)} the proportion of all design discussions in a project to which a developer has contributed which is named as \emph{Coverage} and \noindent\textbf{(c)} the correlation between the coverage and the commit for a particular developer.  

We have organized the paper in the following manner. Section~\ref{sect:related_work} lists some closely related works that are already done. Section~\ref{sect:dataset} describe our dataset on which we are conducting our replication. Section~\ref{sect:replication} explains our replication steps and transitions of the data. Section~\ref{sect:results} briefly discusses the results and the similarity of our result with the original paper. Lastly, Section~\ref{sect:conclusions} gives a summery of our paper and a concluding remark on the original paper that we have replicated. 

